---
title: "AWEAR Case studies analyses"
author: "Julia Thorpe"
date: "September 2018"
output:
  html_document: default
  pdf_document: default
  word_document: default
always_allow_html: yes
---

Some first results from visualising data for all participants.

All of the plots below follow the same format: time along horizontal axis and dates up vertical axis, plotting the entire participation period for each participant. (Note: ignore date at start of all the time axes, which likely show a current or recent date).


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# For solving package install problem: https://stackoverflow.com/questions/5700505/windows-7-update-packages-problem-unable-to-move-temporary-installation
# trace(utils:::unpackPkgZip, edit=TRUE) > line 140 (line 142 in R 3.4.4) > Sys.sleep(0.5) > Sys.sleep(2)

# Load packages and functions.
library(data.table)
library(dtplyr)
library(dplyr)
library(magrittr)
library(lubridate)
library(ggplot2)
library(reshape2)
library(maptools)
library(plotly)
library(maps)
library(mapproj)
library(sp)
library(caTools)
library(geosphere) # added in v3 of data checker
library(mapview) # added in v1 of analysis framework
library(tidyr) # added for function "complete" in assessments section
library(htmltools)
library(RColorBrewer)
#library(processx) # for saving static plotly graphics - NIU 
library("readxl") # For reading in pilot data

# Load custom functions:
#source("./Rscripts/jrt_utils.R")
#source("./Rscripts/jrt_mobility.R")
#source("./Rscripts/jrt_steps.R")
#source("./Rscripts/jrt_activity.R")
#source("./Rscripts/users.R")
source("./Rscripts/stylesheet.R")

# Select participant
#p.codes <- "P03JJ" # single participant
p.codes <- c("P03JJ","P06SS","P07MG","P08UH","P10JL","P13NB") # case studies
```



```{r load_data, echo=FALSE}
# Load any results, set variables etc...
# 
# For A1:
# 
# * screen
# * battery
# * activity.bouts (available)
# * action range (needed) 
# * MCP polys (needed)
# 
# Note: may need windows for heatmap, could avoid heatmap by plotting large markers on scatter which would help with showing data availability

# run load data script 
source("./Rscripts/cases_data_load.R")

source("./Rscripts/cases_plotter_A1.R")
```

## A1. Feasibility

### Device Interaction
Plots showing participants interaction with the phone, including time the screen is on and battery levels/charging patterns (instructions were to charge devices at night).


Screen-on duration plots:
```{r A1_use_screen, eval=FALSE, include=FALSE}


# screen on-off lines (line covering durations that screen is on)
htmltools::tagList(screen.plots)
```


Battery levels/charging patterns:

```{r A1_use_battery, eval=FALSE, include=FALSE}
# battery charging lines (line covering durations that screen is on)
htmltools::tagList(battery.plots.A)
#htmltools::tagList(battery.plots.B)

```

### Behavioural data
Plots showing (a rough idea of) activity and mobility over entire study period. These are meant to give an idea of how much data is available and whether any patterns are evident.

TO ADD: step counts!

Activity bouts
```{r A1_features_act, echo=FALSE}

# All activity bouts over study period
htmltools::tagList(activity.plots)

# All steps over study period
htmltools::tagList(steps.plots)

```

Mobility: plots showing trajectories (stays and moves) along time axis with colour indicating distance from home centroid (in ranges)

```{r A1_features_mob, echo=FALSE}
# Distance from home
htmltools::tagList(mobility.plots)
htmltools::tagList(mcp.plots)

plot_ly() %>%
  add_polygons(data=mcp %>% group_by(participant,dates),
               x=~lon, 
               y=~lat,
               #type="scatter",
               #mode = "lines",
               color = ~participant,
               colors = "Spectral")

# MCP with day colour over a gradient?

# Metrics...?



```


###Adherence & Data availabliity
Describe adherence in terms of how many recording days and es answers there are for the number of days participation

```{r adherence}



es.mobility <- es %>% filter(question_id=="jrt_mobility" | question_id=="mobility_P03")
es.activity <- es %>% filter(question_id=="jrt_activity" | question_id=="activity_P03")

es.adherence.mob <- merge(
  metrics.mob %>% group_by(participant) %>% summarise(data.records=n()),
  es.mobility %>% group_by(participant) %>% summarise(self.reports=n()),
  by="participant"
) %>% 
  mutate(adherence=paste0(round(100*self.reports/data.records),"%"))

es.adherence.act <- merge(
  metrics.act %>% group_by(participant) %>% summarise(data.records=n()),
  es.activity %>% group_by(participant) %>% summarise(self.reports=n()),
  by="participant"
) %>% 
  mutate(adherence=paste0(round(100*self.reports/data.records),"%"))

```

