---
title: "AWEAR Case studies analyses"
author: "Julia Thorpe"
date: "September 2018"
output:
  html_document: default
  word_document: default
  pdf_document: default
always_allow_html: yes
---

# Analysis A2: comparisong between participant perceptions and sensor-based measurement


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# For solving package install problem: https://stackoverflow.com/questions/5700505/windows-7-update-packages-problem-unable-to-move-temporary-installation
# trace(utils:::unpackPkgZip, edit=TRUE) > line 140 (line 142 in R 3.4.4) > Sys.sleep(0.5) > Sys.sleep(2)

# Load packages and functions.
library(data.table)
library(dtplyr)
library(dplyr)
library(magrittr)
library(lubridate)
library(ggplot2)
library(reshape2)
library(maptools)
library(plotly)
library(maps)
library(mapproj)
library(sp)
library(caTools)
library(geosphere) # added in v3 of data checker
library(mapview) # added in v1 of analysis framework
library(tidyr) # added for function "complete" in assessments section
library(htmltools)
library(RColorBrewer)
library("readxl") # For reading in pilot data

# Load custom functions:
source("./Rscripts/stylesheet.R")
source("./Rscripts/JRT_utils.R")

```



```{r data_load, include=FALSE}


p.codes <- c("P03JJ","P06SS","P07MG","P08UH","P10JL","P13NB") # case studies

dist.cutoff <- 100000 # for filtering AR.max to not get holidays 

# # select participant for analysis
# p <- "P10JL"
# 
# # load data for current participant
# p.metrics <- readRDS(paste0("./output_data/metrics_",p,".Rds"))
# p.es <- readRDS(paste0("./output_data/es_",p,".Rds"))

# load complete datasets
source("./Rscripts/cases_data_load.R")

# create required datasets:
es.mobility <- es %>% filter(question_id=="jrt_mobility" | question_id=="mobility_P03")
mobility.compare <- merge(x=metrics.mob, y=es.mobility, by=c("participant", "dates"))

es.activity <- es %>% filter(question_id=="jrt_activity" | question_id=="activity_P03")
activity.compare <- merge(x=metrics.act, y=es.activity, by=c("participant", "dates"))

source("./Rscripts/cases_plotter_A2.R")

```


## Visualising the data as a first impression
* Distributions for each of the metrics
* Filter and repeat

```{r histograms, echo=FALSE}

# MOBILITY
n <- 1
# Spatial
subplot(hist.mob.ar, nrows=n) %>% layout(title="Action range")
subplot(hist.mob.dist, nrows=n) %>% layout(title="Distance covered")
subplot(hist.mob.distfoot, nrows=n) %>% layout(title="Distance covered on foot")
subplot(hist.mob.mcp, nrows=n) %>% layout(title="Minimum convex polygon")

# Spatial - Filtered
subplot(hist.mob.ar.f, nrows=n) %>% layout(title="Action range (filtered)")
subplot(hist.mob.dist.f, nrows=n) %>% layout(title="Distance covered (filtered)")
subplot(hist.mob.mcp.f, nrows=n) %>% layout(title="Minimum convex polygon (filtered)")

# Temporal
subplot(hist.mob.Tmove, nrows=n) %>% layout(title="Time spent moving between places")
subplot(hist.mob.Tout, nrows=n) %>% layout(title="Time spent out of home")

# Counts
subplot(hist.mob.Nplace, nrows=n) %>% layout(title="Number of unique places visited")
subplot(hist.mob.Nmove, nrows=n) %>% layout(title="Number of moves between places")

# ACTIVITY

# steps:
# total steps
subplot(hist.act.steps, nrows=n) %>% layout(title="Daily stepcount") # PROBLEMS! FIXED :)
subplot(hist.act.Tactive, nrows=n) %>% layout(title="Time spent on foot/bike") 
subplot(hist.act.Nactive, nrows=n) %>% layout(title="Number of foot/bike bouts") 
subplot(hist.act.Tstill, nrows=n) %>% layout(title="Time spent still between 6am and 10pm") 

remove(
  hist.act.Nactive,
  hist.act.steps,
  hist.act.Tactive,
  hist.act.Tstill,
  hist.mob.ar,
  hist.mob.ar.f,
  hist.mob.dist,
  hist.mob.dist.f,
  hist.mob.mcp,
  hist.mob.mcp.f,
  hist.mob.Nmove,
  hist.mob.Nplace,
  hist.mob.Tmove,
  hist.mob.Tout
)

```

## Relation between data and ES
Show ranges of each variable against the answers

```{r es_metrics_spread, echo=FALSE}

# mobility answers + metrics:
subplot(range.compare.ar, shareY=TRUE) %>% layout(title="Action Range")
subplot(range.compare.dist, shareY=TRUE) %>% layout(title="Distance covered in moves")
subplot(range.compare.distfoot, shareY=TRUE) %>% layout(title="Distance covered on foot")
subplot(range.compare.mcp, shareY=TRUE) %>% layout(title="MCP")

subplot(range.compare.Tout, shareY=TRUE) %>% layout(title="Time out of home")
subplot(range.compare.Tmove, shareY=TRUE) %>% layout(title="Time moving")

subplot(range.compare.Nplaces, shareY=TRUE) %>% layout(title="N places")
subplot(range.compare.Nmoves, shareY=TRUE) %>% layout(title="N moves")

subplot(range.compare.activeT, shareY=TRUE) %>% layout(title="Active Time")
subplot(range.compare.activeB, shareY=TRUE) %>% layout(title="N active bouts")
subplot(range.compare.still, shareY=TRUE) %>% layout(title="Still periods")
subplot(range.compare.steps, shareY=TRUE) %>% layout(title="Steps")

remove(
  range.compare.ar,
  range.compare.dist,
  range.compare.mcp,
  range.compare.Nmoves,
  range.compare.Nplaces,
  range.compare.Tmove,
  range.compare.Tout,
  range.compare.activeT,
  range.compare.activeB,
  range.compare.still,
  range.compare.steps
)

# # For single participant
# p.es.mob <- p.es %>% filter(question_id=="jrt_mobility")
# p.compare.mob <- merge(x=p.metrics, y=p.es.mob, by="dates")
# 
# plot_ly(p.compare.mob %>% group_by(answer),
#         x=~AR.max,
#         y=~answer,
#         type = "scatter",
#         mode = "markers+lines") %>%
#   add_trace(x=~dist.total)
# 
# plot_ly(p.compare.mob %>% group_by(answer),
#         x=~Tt.move,
#         y=~answer,
#         type = "scatter",
#         mode = "markers+lines") %>%
#   add_trace(x=~Tt.out)
# 
# plot_ly(p.compare.mob %>% group_by(answer),
#         x=~N.places,
#         y=~answer,
#         type = "scatter",
#         mode = "markers+lines") %>%
#   add_trace(x=~N.moves)


```

Convert the metrics to scores and compare with ES answers directly, could include:

* Table showing which is most correlated (should end up demonstrating that a combination is best)
* Spatial, Temporal and Counts (not converted to scores, different approach) + combination
* Activity (bouts, time) and steps + combination

```{r scoring, echo=FALSE, warning=FALSE}

# subplot(mob.probs, nrows=6) %>% layout(title="comparison with probabilities - mobility")
# mob.probs[[1]]
# subplot(act.probs, nrows=6) %>% layout(title="comparison with probabilities - activity")
# act.probs[[3]]

mob.probs[[1]]
mob.probs[[2]]
mob.probs[[3]]
mob.probs[[4]]
mob.probs[[5]]
mob.probs[[6]]


# subplot(mob.scores[[1]],mob.probs[[1]])
# subplot(act.scores[[3]],act.probs[[3]])

act.probs[[1]]
act.probs[[2]]
act.probs[[3]]
act.probs[[4]]
act.probs[[5]]
act.probs[[6]]



subplot(mob.probs[[1]],act.probs[[1]],nrows=2)


# tester<- metrics.mob %>%
#   group_by(participant) %>%
#   do(quantile(.$AR.max, probs = prbs) %>% data.frame() %>% tibble::rownames_to_column("Q")) %>% 
#   rename(AR.max.q = ".")
# 
# test %>% summarise(ar.max.diff = mean(abs(AR.max.score-answer)),
#                    dist.total.diff = mean(abs(dist.total.score-answer)),
#                    mcp.diff = mean(abs(mcp.score-answer)),
#                    Tt.move.diff = mean(abs(Tt.move.score-answer)),
#                    Tt.out.diff = mean(abs(Tt.out.score-answer)),
#                    combo.diff = mean(abs(combo-answer)))



```


Comparison with baseline data: 
(discarded - will instead use questionnaires as background information otherwise just crowds the results)

```{r compare_assess, echo=FALSE}
# analyses cut from last paper here (potentially)

```

## Comparison between perceived and objectively measured individual goal attainment

### Goal: To get out of the house every day 

Example: P07MG
```{r goal_p07, echo=FALSE, warning=FALSE}

# import participant reported goal attainment
p07.perceived <- c(1,0,0,1,0,-1,1,1)

# measure from metrics/data
p07.metrics.mob <- 
  metrics.mob %>% filter(participant == "P07MG") %>%
  #mutate(day = ifelse(day<8,day,day-4)) %>%
  mutate(week = ((day-1) %/% 7)+1)

p07.metrics.act <- 
  metrics.act %>% filter(participant == "P07MG") %>%
  mutate(day = p07.metrics.mob$day,
         week = p07.metrics.mob$week)

# Tabulate results by week
p07.tab.mob <- p07.metrics.mob %>% group_by(week) %>%
  summarise( Ndays = n(),
             move.days = sum(N.moves > 0),
             T.move.ave = round(mean(Tt.move*60)),
             date = max(dates)) %>%
  mutate(SR.goal = c(p07.perceived,NA))

p07.tab.act <- p07.metrics.act %>% group_by(week) %>%
  summarise( Ndays = n(),
             T.active.ave = round(mean(active.time)),
             steps = round(mean(steps)))

p07.weekly.results <- cbind(p07.tab.mob[1:8,], p07.tab.act[1:8,3:4]) %>% 
  select(week, move.days,SR.goal)

p07.weekly.results

remove(p07.metrics.mob, p07.metrics.act, p07.tab.act, p07.tab.mob, p07.weekly.results, p07.perceived)

```

Example: P13NB
```{r goal_p13, echo=FALSE, warning=FALSE}

# import participant reported goal attainment
p13.perceived <- c(0,1,0,1,0,0,0,0)

# measure from metrics/data
p13.metrics.mob <-
  metrics.mob %>% filter(participant == "P13NB") %>%
  mutate(week = ((day-1) %/% 7)+1)
 
p13.metrics.act <-
  metrics.act %>% filter(participant == "P13NB")

p13.metrics <- merge(p13.metrics.mob,
                     p13.metrics.act,
                     by=c("dates", "participant"),
                     all=T)

T.move.pfunc <- ecdf(p13.metrics$Tt.move)
steps.pfunc <- ecdf(p13.metrics$steps)

# Tabulate results by week
p13.weekly.results <- p13.metrics %>% group_by(week) %>%
  summarise( Ndays = n(),
             move.days = sum(N.moves > 0),
             T.move.ave = round(mean(Tt.move*60)),
             T.active.ave = round(mean(active.time)),
             steps = round(mean(steps)),
             date = max(dates)) %>%
  mutate(SR.goal = c(p13.perceived,NA),
         steps.prb = steps.pfunc(steps) %>% round(2),
         T.move.prb = T.move.pfunc(T.move.ave/60) %>% round(2))

p13.weekly.results[1:8,] %>% select(week, move.days,T.move.ave,T.move.prb,steps,steps.prb,SR.goal)

plot_ly(p13.weekly.results[1:8,],
        x = ~week,
        y = ~SR.goal,
        type = "scatter",
        mode = "markers",
        marker = list(size=12, color = "red"),
        name = "Goal attainmnet",
        width = 900,
        height = 210) %>%
  add_bars(y = ~SR.goal, width=0.1, showlegend = FALSE) %>%
  add_trace(y = ~(T.move.prb-0.5)*2,
            mode = "markers+lines",
            marker = list(size=2, color =  greys[5]),
            line = list(width = 2, color =  greys[5],dash = "dot"), 
            name = "Average time moving") %>%
  add_trace(y = ~(steps.prb-0.5)*2,
            mode = "markers+lines",
            marker = list(size=2, color = greys[3]),
            line = list(width = 2, color =  greys[3],dash = "dash"), 
            name = "Steps") %>%
  layout(yaxis = list(title = "Goal rating | Probability-0.5"))

remove(p13.metrics, p13.weekly.results, T.move.pfunc, steps.pfunc, p13.perceived)


```

### Goal: walk longer daily (more/less activity X)

Example: P06SS
```{r goal_p06, echo=FALSE, warning=FALSE}

# import participant reported goal attainment
p06.perceived <- c(-1,0,0,1,NA,-1,NA,-1,-1,NA,-1,NA)
p06.calldates <- as.Date(c(
  "23-03-2018", 
  "03-04-2018",
  "10-04-2018",
  "17-04-2018",
  "24-04-2018", NA,
  "01-05-2018",
"08-05-2018",
"17-05-2018",
"23-05-2018",
"04-06-2018", NA), format = "%d-%m-%Y")


# measure from metrics/data
p06.metrics.mob <-
  metrics.mob %>% filter(participant == "P06SS")

p06.metrics.act <-
  merge(
    metrics.act %>% filter(participant == "P06SS"),
    act.pday %>% filter(participant == "P06SS", activity == "Foot"),
    by=c("dates", "participant"),
    all=T
  )

p06.metrics <- merge(p06.metrics.mob,
                     p06.metrics.act,
                     by=c("dates", "participant"),
                     all=T)
remove(p06.metrics.mob,p06.metrics.act)

# adjust the dates to get weeks that match phonecalls (remove days 8-11, then calculate study weeks, which are not continuous calendar weeks)
p06.metrics %<>% filter( day < 8 | day > 11 ) %>%
  mutate(day = c(1:n())) %>%
  mutate(week = ((day-1) %/% 7)+1)

# Create probability functions
T.foot.pfunc <- ecdf(p06.metrics$total.time)
steps.pfunc <- ecdf(p06.metrics$steps)

# Tabulate results by week
p06.weekly.results <- p06.metrics %>% group_by(week) %>%
  summarise( #Ndays = n(),
             still.time.mean = round(mean(still.time, na.rm = T)), # still periods 
             walk.time.mean = round(mean(total.time, na.rm = T)), # time on foot (might need to replaces NA with 0)
             steps = round(mean(steps, na.rm = T)), # steps
             date = max(dates)) %>%
  mutate(walk.Q = T.foot.pfunc(walk.time.mean) %>% round(2),
         steps.Q = steps.pfunc(steps) %>% round(2)) %>%
  mutate(SR.goal = p06.perceived)

p06.weekly.results[1:11,] %>% select(week,walk.time.mean,steps,walk.Q,steps.Q,SR.goal)

# Plot results
plot_ly(p06.weekly.results,
        x = ~week,
        y = ~SR.goal,
        type = "scatter",
        mode = "markers",
        marker = list(size=12, color = "red"),
        name = "Goal attainment",
        width = 900,
        height = 210) %>%
  add_bars(y = ~SR.goal, width=0.1, showlegend = FALSE) %>%
  add_trace(y = ~(steps.Q-0.5)*2,
            mode = "markers+lines",
            marker = list(size=2, color =  greys[5]),
            line = list(width = 2, color =  greys[5],dash = "dot"),
            name = "Steps") %>%
  add_trace(y = ~(walk.Q-0.5)*2,
            mode = "markers+lines",
            marker = list(size=2, color = greys[3]),
            line = list(width = 2, color =  greys[3],dash = "dash"),
            name = "Walk time") %>%
  layout(yaxis = list(title = "Goal rating | Probability-0.5"),
         xaxis = list(dtick = 1))


```

Example: P08UH
Goal to drive less and ride bike more (at least 4 days per week), but towars the start focused instead on walking or other activities. During a weekly call on the 17th April said he started biking that day.

```{r goal_p08, echo=FALSE, warning=FALSE}
# perceived goal attainment
p08.perceived <- c(-1,-1,0,NA,-1,0,0,0)

# get all recorded dates/days for participant
p08.metrics <- metrics.mob %>% filter(participant == "P08UH") %>%
  select(participant, dates, day) %>% 
  mutate(day = day-7) %>% # to match dates of weekly calls
  filter(day > 0)

p08.bike <- act.pday %>% filter(participant == "P08UH", activity == "Bicycle")
p08.vehicle <- act.pday %>% filter(participant == "P08UH", activity == "Vehicle")
p08.trans <- merge(x = p08.bike, y = p08.vehicle, by=c("participant","dates"), all=TRUE, suffixes=c(".bike",".vehicle")); remove(p08.bike, p08.vehicle)

p08.goals <- 
  merge(p08.metrics, p08.trans, by=c("participant","dates"), all.x=TRUE) %>%
  select(dates, day, total.time.bike, N.bike, total.time.vehicle, N.vehicle) %>%
  mutate(week = ((day-1) %/% 7)+1)
#remove(p08.metrics,p08.trans)

p08.goals[is.na(p08.goals)] <- 0

p08.weekly.results <- p08.goals %>% filter(week < 9) %>%
  group_by(week) %>%
  summarise(dates = max(dates),
            Ndays = n(),      # just to check there are 7 days being measured in each study week
            bike.days = sum(N.bike>0),
            vehicle.days = sum(N.vehicle>0),
            bike.time.alt = (sum(total.time.bike)/sum(N.bike>0)) %>% round(2),
            bike.time = (sum(total.time.bike)) %>% round(),
            vehicle.time = (sum(total.time.vehicle)) %>% round()) %>%
  mutate(SR.goal = p08.perceived)

p08.weekly.results %>% select(week, dates, bike.days, vehicle.days, bike.time, bike.time.alt, vehicle.time, SR.goal)

```


### Goal: activity schedule

Example: P10JL
Could add annotations to the timeline with weekly call notes

```{r goal_p10, echo=FALSE, warning=FALSE}

# Monday-Friday 1 hour at the training place.

# get the stays, test if they are close to X and duration.
p10.traj.summary <- readRDS("./output_data/traj_goal_P10JL.Rds")
training.loc <- c(12.444629, 55.627071) # lon, lat
  
proximity <- distGeo(p10.traj.summary %>% select(clon,clat),
        training.loc,
        a=6378137, f=1/298.257223563)
p10.traj.summary %<>%
  mutate(prox = proximity) %>%
  mutate(is.training = prox < 150) #threshold within which a stay is considered at the training centre

p10.training.days <- p10.traj.summary %>% group_by(dates) %>%
  summarise(
    training = sum(is.training, na.rm = TRUE),
    training.time = sum(durations[is.training],na.rm = TRUE)
  ) %>%
  mutate(weekday = weekdays(dates))

remove(proximity, training.loc)

# # Examine data to determine threshold
# plot_ly(p10.traj.summary,
#         x = ~T.start,
#         y = ~proximity)


# Get dates and perceived goals
p10.SR <- data.frame(
  perceived = c(0,1,0,NA,NA,0,0,-1,1,0,0),
  dates = as.Date(c("19-03-2018",
                           "26-03-2018",
                           "03-04-2018",
                           "10-04-2018",
                           "17-04-2018",
                           "24-04-2018",
                           "02-05-2018",
                           "08-05-2018",
                           "15-05-2018",
                           "22-05-2018",
                           "29-05-2018"),
                         format = "%d-%m-%Y"),
    notes = c("weather dependent",
              " ",
              "holidays, centre closed",
              "Stopped using watch",
              NA,
              "All activities",
              "All activities",
              "Distruptions, social",
              "Stepcount 18000 today",
              "Long walk the 18th",
              "Too warm / public holidays"))

p10.goals <- merge(p10.training.days,
                   p10.SR,
                   by="dates",
                   all= T) %>%
  tail(83) %>% # to align with call dates
  mutate(day = c(0,cumsum(diff(dates)%>%as.numeric()))+1) %>%
  mutate(week = ((day-1) %/% 7)+1)

plot_ly(data = p10.goals,
        x = ~dates,
        y = ~training.time/60,
        type = "bar",
        marker = list(color = "lightblue"),
        width = 1500) %>%
  add_trace(y = ~perceived, marker = list(color = "black"), showlegend = FALSE) %>%
  add_trace(y = ~perceived, type = "scatter", mode = "markers", marker = list(color = "black", size = 6, symbol="square"), showlegend = FALSE) %>%
  add_text(data = p10.SR,
           x=~dates,
           y=~perceived,
           text = ~notes,
           inherit=FALSE,
           textposition = ~ifelse(perceived<0,"bottom centre","top centre"),
           textfont = list(color = "black", size = 12))

# plot_ly(data = p10.goals,
#         x = ~dates,
#         y = ~perceived,
#         type = "scatter",
#         mode = "markers",
#         marker = list(color = "black", size = 4),
#         width = 1500) %>%
#   add_bars(y = ~perceived, width = 0.01, showlegend = FALSE) %>%
#   add_trace(y = ~perceived, type = "scatter", mode = "markers", marker = list(color = "black", size = 12), showlegend = FALSE) %>%
#   add_text(data = p10.SR, 
#            x=~dates, 
#            y=~perceived,
#            text = ~notes,
#            inherit=FALSE,
#            textposition = "bottom centre",
#            textfont = list(color = "black", size = 12))

# plot_ly(data = p10.goals,
#         x = ~dates,
#         y = ~training.time/60,
#         type = "scatter",
#         mode = "lines+markers") %>%
#   add_trace(data = p10.goals %>% filter(!is.na(perceived)),
#         x = ~dates,
#         y = ~perceived,
#         inherit = F,
#         type = "scatter",
#         mode = "markers") %>%
#   add_trace(data = p10.goals %>% filter(!is.na(perceived)),
#         x = ~dates,
#         y = ~perceived,
#         inherit = F,
#         type = "bar")

# summarise in a table
p10.goal.results <- p10.goals %>% group_by(week) %>%
  summarise(dates = max(dates),
            training = sum(training > 0),
            total.time = sum(training.time/60) %>% as.numeric() %>% round()) %>%
  mutate(SR.goal = c(p10.SR$perceived,NA))

p10.goal.results[c(1:2,6:11),]


```




