---
title: "AWEAR Case studies analyses"
author: "Julia Thorpe"
date: "September 2018"
output:
  html_document: default
  pdf_document: default
  word_document: default
always_allow_html: yes
---

Some first results from visualising data for all participants.

All of the plots below follow the same format: time along horizontal axis and dates up vertical axis, plotting the entire participation period for each participant. (Note: ignore date at start of all the time axes, which likely show a current or recent date).


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# For solving package install problem: https://stackoverflow.com/questions/5700505/windows-7-update-packages-problem-unable-to-move-temporary-installation
# trace(utils:::unpackPkgZip, edit=TRUE) > line 140 (line 142 in R 3.4.4) > Sys.sleep(0.5) > Sys.sleep(2)

# Load packages and functions.
library(data.table)
library(dtplyr)
library(dplyr)
library(magrittr)
library(lubridate)
library(ggplot2)
library(reshape2)
library(maptools)
library(plotly)
library(maps)
library(mapproj)
library(sp)
library(caTools)
library(geosphere) # added in v3 of data checker
library(mapview) # added in v1 of analysis framework
library(tidyr) # added for function "complete" in assessments section
library(htmltools)
library(RColorBrewer)
library("readxl") # For reading in pilot data

# Load custom functions:
source("./Rscripts/stylesheet.R")
source("./Rscripts/JRT_utils.R")

```

Possibly merge all results from all participants into one dataset to make it easier to plot the various subsets. These should include a row per day per participant with the following columnns:

* all mobility metrics
* ES answers
* metrics derived from acitivity bouts (e.g. still periods, use of bike/foot/vehicle as transport)
* daily stepcount (watch and phone each own column)


```{r data_load}


p.codes <- c("P03JJ","P06SS","P07MG","P08UH","P10JL","P13NB") # case studies

# # select participant for analysis
# p <- "P10JL"
# 
# # load data for current participant
# p.metrics <- readRDS(paste0("./output_data/metrics_",p,".Rds"))
# p.es <- readRDS(paste0("./output_data/es_",p,".Rds"))

# load complete datasets
source("./Rscripts/cases_data_load.R")
source("./Rscripts/cases_plotter_A2.R")

```


Visualising the data as a first impression
* Distributions for each of the metrics
* Filter and repeat

```{r}



# MOBILITY

# dataset metrics.mob, go through all metrics for all participants.
subplot(hist.mob.ar)
subplot(hist.mob.dist)
subplot(hist.mob.mcp)
subplot(hist.mob.Tmove)
subplot(hist.mob.Tout)
subplot(hist.mob.Nplace)
subplot(hist.mob.Nmove)

# b <- 100
# # spatial
# hist(p.metrics$AR.max/1000, breaks=b)
# hist(p.metrics$dist.total/1000, breaks=b)
# hist(p.metrics$mcp.area, breaks=b)
# 
# 
# p.ar <- plot_ly(x =p.metrics$AR.max/1000, type = "histogram")
# p.dt <- plot_ly(x =p.metrics$dist.total/1000, type = "histogram")
# 
# subplot(p.ar,p.dt)
# 
# # temporal
# hist(as.numeric(p.metrics$Tt.move), breaks=48)
# hist(as.numeric(p.metrics$Tt.out), breaks=48)
# 
# # count
# hist(p.metrics$N.places, breaks=10)
# hist(p.metrics$N.moves, breaks=10)

# ACTIVITY

# steps

# bouts





```

Now filter the data and repeat

```{r}


p.metrics.filt <- p.metrics %>% filter(AR.max < 20000)
b <-20
hist(p.metrics.filt$AR.max, breaks=b)
hist(p.metrics.filt$AR.mean, breaks=b)
hist(p.metrics.filt$dist.total, breaks=b)
hist(p.metrics.filt$dist.max, breaks=b)
hist(p.metrics.filt$mcp.area, breaks=b)

hist(as.numeric(p.metrics.filt$Tt.move), breaks=48)
hist(as.numeric(p.metrics.filt$Tt.out), breaks=48)


prbs <- c(1:5)/5
quantile(p.metrics.filt$AR.max, probs = prbs)
quantile(p.metrics.filt$dist.total, probs = prbs)

```
Now look at relation between data and ES

* Show ranges of each variable against the answers (could have a plot per metrics including all participants as traces)

TO ADD: ES activity answers and
* step counts, watch/phone (whichever is higher) 
* still periods 


```{r}

p.es.mob <- p.es %>% filter(question_id=="jrt_mobility")
p.compare.mob <- merge(x=p.metrics.filt, y=p.es.mob, by="dates")

plot_ly(p.compare.mob %>% group_by(answer),
        x=~AR.max,
        y=~answer,
        type = "scatter",
        mode = "markers+lines") %>%
  add_trace(x=~dist.total)

plot_ly(p.compare.mob %>% group_by(answer),
        x=~Tt.move,
        y=~answer,
        type = "scatter",
        mode = "markers+lines") %>%
  add_trace(x=~Tt.out)

plot_ly(p.compare.mob %>% group_by(answer),
        x=~N.places,
        y=~answer,
        type = "scatter",
        mode = "markers+lines") %>%
  add_trace(x=~N.moves)


```
Convert the metrics to scores and compare with ES answers directly, include:
* Table showing which is most correlated (should end up demonstrating that a combo is best)
* Spatial, Temporal and Counts (not sure about counts?!)

Could make "distance", "temporal" and "count" scores and one total overall combo

TO ADD: convert activity features to scores, including:
* step counts, watch/phone (whichever is higher) 
* still periods 

Compare with activity scores as per other plots.


```{r convert}


test <- p.compare.mob %>% mutate(
  AR.max.score = score_converter(p.compare.mob$AR.max, N=5),
  dist.total.score = score_converter(p.compare.mob$dist.total, N=5),
  mcp.score = score_converter(p.compare.mob$mcp.area %>% as.numeric(), N=5),
  Tt.move.score = score_converter(p.compare.mob$Tt.move %>% as.numeric(), N=5),
  Tt.out.score = score_converter(p.compare.mob$Tt.out %>% as.numeric(), N=5)
)

test %<>% mutate(combo = (AR.max.score+dist.total.score+Tt.move.score+Tt.out.score)/4)

# AR.max.score <- score_converter(p.compare.mob$AR.max, N=5)
# dist.total.score <- score_converter(p.compare.mob$dist.total, N=5)
# Tt.move.score <- score_converter(p.compare.mob$Tt.move %>% as.numeric(), N=5)
# Tt.out.score <- score_converter(p.compare.mob$Tt.out %>% as.numeric(), N=5)
# 
# test <- cbind(p.compare.mob$dates,
#               p.compare.mob$answer,
#               AR.max.score,
#               dist.total.score,
#               Tt.move.score,
#               Tt.out.score) %>% as.data.frame()

plot_ly(test,
        x=~dates,
        y=~answer,
        type = "scatter",
        mode = "lines",
        line = list(color="red", width=6),
        width = 1500) %>%
  add_trace(y=~AR.max.score, line = list(color="cyan", width=2)) %>%
  add_trace(y=~dist.total.score, line = list(color="lightblue", width=2)) %>%
  add_trace(y=~Tt.move.score, line = list(color="blue", width=2)) %>%
  add_trace(y=~Tt.out.score, line = list(color="darkblue", width=2)) %>%
  add_trace(y=~combo, line = list(color="green", width=4))

test %>% summarise(ar.max.diff = mean(abs(AR.max.score-answer)),
                   dist.total.diff = mean(abs(dist.total.score-answer)),
                   mcp.diff = mean(abs(mcp.score-answer)),
                   Tt.move.diff = mean(abs(Tt.move.score-answer)),
                   Tt.out.diff = mean(abs(Tt.out.score-answer)),
                   combo.diff = mean(abs(combo-answer)))

plot_ly(test,
        x=~AR.max,
        y=~Tt.out,
        type = "scatter",
        mode = "markers",
        color = ~answer, 
        marker = list(size=15))

plot_ly(test,
        x=~dist.total,
        y=~Tt.out,
        type = "scatter",
        mode = "markers",
        color = ~answer, 
        marker = list(size=15))

plot_ly(test,
        x=~N.places,
        y=~N.stay.out,
        type = "scatter",
        mode = "markers",
        color = ~answer, 
        marker = list(size=15))

plot_ly(test,
        x=~dates,
        y=~answer/max(answer),
        type = "scatter",
        mode = "lines",
        line = list(color="red", width=6),
        width = 1500) %>%
  add_trace(y=~N.stay.out/max(N.stay.out), line = list(color="cyan", width=2)) %>%
  add_trace(y=~N.places/max(N.places), line = list(color="lightblue", width=2))






```

Comparison with baseline data:

* mobility zones (LSA)
* activity: transport and still periods (GPAQ)