---
title: "Engineering systems design in healthcare - Behavioural feature extraction"
author: "Julia Thorpe"
institution: "Engineering Systems Division, DTU Management"
date: "October 2018"
output: html_document
---

This work is conducted as part of the PhD project "Engineering Systems Design in Healthcare" at the Technical University of Denmark (DTU) in collaboration with Rigshospitalet-Glostrup. The project investigates the use of smart mobile and wearable technology for support and monitoring in dementia rehabilitation. The code below is used to extract a set of mobility features from location data and activity features from recognised activity and step count data.


## Setup

Loads required packages and custom functions

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load packages and functions.
library(data.table)
library(dtplyr)
library(dplyr)
library(magrittr)
library(lubridate)
library(ggplot2)
library(reshape2)
library(maptools)
library(plotly)
library(maps)
library(mapproj)
library(sp)
library(caTools)
library(geosphere) 
library(mapview) 
library(tidyr) 
library(htmltools)
library(RColorBrewer)
#library(processx) # for saving static plotly graphics - NIU 
library("readxl") # for reading in pilot data

# For DBSCAN clustering
library(fpc)
library(dbscan)
library(factoextra)

# Load custom functions:
source("./Rscripts/jrt_utils.R")
source("./Rscripts/jrt_mobility.R")
source("./Rscripts/jrt_steps.R")
source("./Rscripts/jrt_activity.R")
source("./Rscripts/users.R")
source("./Rscripts/stylesheet.R")

```


Select participants to include and set input variables for the feature extraction algorithms:

```{r Define variables}

# Select participant
p.codes <- c("P03JJ", "P06SS", "P07MG", "P08UH", "P10JL", "P13NB") # case studies
#p.codes <- c("daisy","violet","agapantha","anthurium","nasturtium") # pilot

# Mobility:
loc.accuracy <- 25  # threshold for accuracy of location points in meters
dT <- 5             # delta T, time window in minutes
dD <- 100           # delta D, diagonal distance boundary in meters
time.threshold.stay <- 10 # minimum duration of a stay, in minutes
time.threshold.go <- 5    # cut-off for filtering out "go" events to/from same location, in minutes
dist.threshold <- 50      # distance in meters within which two centriods belong to same stay location
Qd <- .99                 # quantile of distances to include in the MC polygon
#doi <- as.POSIXct("2018-01-30") # day of interest (use when not d.start)

# Steps:
win.size <- 15 # window size in minutes

# Activity:
acts <- c("Still", "Foot", "Vehicle", "Bicycle") # specify activities of interest


```


Save device data that used for other purposes than extracting behavioural features (battery, screen, mobile self-reports).

```{r direct_save, eval=FALSE, include=FALSE}

for(p in p.codes){
  
  # unpack participant data
  P <- participants[[p]]
  list2env(P, .GlobalEnv)
  remove(P)
  d.study <-
  as.numeric(round(difftime(d.stop, d.start, units = "days")))
  datasets.all <-
  readRDS(paste0("./output_data/datasets_", p, ".Rds"))
  
  # battery
  p.battery <- datasets.all$battery %>%
  select(timestamp, dates, times, plugged, status, level) %>%
  mutate(participant = p)
  #saveRDS(p.battery, paste0("./output_data/battery_", p, ".Rds"))
  
  # screen
  p.screen <- datasets.all$screen %>%
  select(timestamp, dates, times, screen_on) %>%
  mutate(participant = p)
  #saveRDS(p.screen, paste0("./output_data/screen_", p, ".Rds"))
  
  # experience sampling
  p.es <- datasets.all$experience_sampling %>%
  select(timestamp, dates, times, question_id, answer) %>%
  mutate(participant = p)
  #saveRDS(p.es, paste0("./output_data/es_", p, ".Rds"))

}

```

## Feature extraction

### Mobility Features
Location data is used to extract mobility features. Inputs include a GPS log file (dataframe) with the following columns: 
*timestamp
*

```{r MOBILITY}

for(p in p.codes){
  
  # unpack participant data
  P <- participants[[p]]
  list2env(P, .GlobalEnv); remove(P)
  d.study <-  as.numeric(round(difftime(d.stop, d.start, units = "days"))) # participation period
  datasets.all <-  readRDS(paste0("./output_data/datasets_", p, ".Rds"))
  
  # get location data
  gps.log <- datasets.all$location %>%
  filter(accuracy <= loc.accuracy) %>% # filter low accuracy GPS readings
  select(lat, lon, timestamp, intervals.alt, dates, times)
  
  # get distances between points
  gps.log %<>% mutate(displacements = 
                        c(0, distGeo(gps.log %>% select(lon, lat),
                                     a = 6378137, f = 1 / 298.257223563)))
  
  # get trajectories and metrics
  source("./Rscripts/mod_traj.R")
  mob.metrics <- get_metrics(traj.summary, gps.traj)
  mob.zones <- mobility_zones(traj.summary)

# #  save results
# 
# 
# # p.homedist <- gps.traj %>% select(timestamp, dates, times, homedist) %>%
# #   mutate(participant = p)
# # saveRDS(p.homedist,paste0("./output_data/homedist_",p,".Rds"))
# 
# p.traj <- traj.summary %>% select(dates,
#                                   T.start, T.end, durations,
#                                   traj.event, is.stay, loc.id,
#                                   is.home, action.range) %>%
#   mutate(participant = p)
# saveRDS(p.traj,paste0("./output_data/traj_",p,".Rds"))
# 
# # p10.traj <- traj.summary %>% select(dates,
# #                                   T.start, T.end, durations,
# #                                   traj.event, is.stay, loc.id,
# #                                   clat,clon, # included to test whether visiting the training centre
# #                                   is.home, action.range) %>%
# #   mutate(participant = p)
# # saveRDS(p10.traj,paste0("./output_data/traj_goal_",p,".Rds"))
# 
# p.metrics <- mob.metrics %>% select(dates, Tt.out, N.places) %>%
#   #filter(dates < as.POSIXct("2018-06-24") | dates > as.POSIXct("2018-07-06")) %>% # for Nina only
#   mutate(day=c(1:nrow(mob.metrics)), participant = p)
# saveRDS(p.metrics,paste0("./output_data/metrics_",p,".Rds"))
# 
# saveRDS(mob.zones,paste0("./output_data/mobilityzones_",p,".Rds"))

p.metrics <- mob.metrics %>%
  mutate(day=c(1:nrow(mob.metrics)), participant = p)
saveRDS(p.metrics,paste0("./output_data/metrics_",p,".Rds"))

# # p.mcp.points <- do(gps.log %>% group_by(dates), get_mcp_points(.)) %>%
# #   mutate(participant = p)
# # saveRDS(p.mcp.points,paste0("./output_data/mcp_",p,".Rds"))

}


# clear environment
#remove(loc.accuracy, dT, dD, time.threshold.stay, time.threshold.go, dist.threshold, Qd)
```

### Steps

```{r STEPS}

#, eval=FALSE, include=FALSE

for(p in p.codes){
  P <- participants[[p]]
  list2env(P, .GlobalEnv); remove(P)
  d.study <- as.numeric(round(difftime(d.stop,d.start,units="days")))
  datasets.all <- readRDS(paste0("./output_data/datasets_",p,".Rds"))

# get data
steps.log <- datasets.all$step_count %>% 
  select(step_count, dsource, timestamp, intervals.alt, dates, times)

# calculate results
source("./Rscripts/mod_steps.R") # calculate step counts by day
steps.win <- pattern_steps(steps.watch %>% ungroup(), win.size = win.size) # counts steps by time windows over the day

# save results: 
# phone and watch cumulative count over day
stepcounters <- rbind(steps.watch %>% ungroup() %>% select(dates, timestamp, stepcounter) %>% mutate(source="watch"),
                      steps.phone %>% ungroup() %>% select(dates, timestamp,stepcounter) %>% mutate(source="phone")) %>%
  mutate(participant = p)
saveRDS(stepcounters,paste0("./output_data/stepcounters_",p,".Rds"))

# total counts per day
saveRDS(steps.totals %>% mutate(participant = p),
  paste0("./output_data/steptotals_",p,".Rds"))

} 

# clear environment
remove(win.size, steps.log)
```

### Activity Features

```{r ACTIVITY}

for(p in p.codes){
  P <- participants[[p]]
  list2env(P, .GlobalEnv); remove(P)
  d.study <- as.numeric(round(difftime(d.stop,d.start,units="days")))
  datasets.all <- readRDS(paste0("./output_data/datasets_",p,".Rds"))
  
# get data
activity.log <- datasets.all$activity %>% filter(label %in% acts)
# To look at only "active" time of day
#   filter(times > as.POSIXct(x="06:00:00",format="%H:%M:%S",tz="CET"),  
#          times < as.POSIXct(x="22:00:00",format="%H:%M:%S",tz="CET"))

# Keep only the entries with max confidence for each timestamp (can still result in multiple activities per timestamp if several at same time have same (max) confidence)
before <- nrow(activity.log)
activity.log %<>% 
  group_by(timestamp) %>% filter(confidence == max(confidence)) %>% 
  ungroup() %>% as.data.frame()
after <- nrow(activity.log)
cat("Complete: activity data reduced by ", 100-(100*after/before), "% by keeping only the max confidence for each unique timestamp \n");

# calculate bouts
activity.bouts <- activity_bouts(activity.log, acts); remove(activity.log)
activity.bouts %<>% filter(size>1)

# summarise by day
activity.bouts.pday <- activity.bouts %>% group_by(dates, activity) %>% 
  summarise(total.time =  sum(duration), N = n()) %>%
  mutate(mean.duration = total.time/N)

# For comparison with assessments [NIU]

# get traj results saved in mobility chunk:
traj.summary <-  readRDS(paste0("./output_data/traj_",p,".Rds"))

# indicate whether activity bouts overlap with a move
activity.moves <- bout_moves(activity.bouts, traj.summary)

# daily summary for activity bouts with stay/move information
activity.moves.pday <- activity.moves %>%
  group_by(dates, activity, moving) %>%
  summarise(total.time = sum(duration))

# save results
saveRDS(activity.bouts %>% mutate(participant=p),paste0("./output_data/activity_",p,".Rds"))
saveRDS(activity.bouts.pday %>% mutate(participant=p),paste0("./output_data/activity_pday_",p,".Rds"))
saveRDS(activity.moves.pday %>% mutate(participant=p),paste0("./output_data/activity_moves_pday_",p,".Rds"))

}

```


